### 2017-04-05 paper/evaluation.tex
another pass on RQ1

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\footnote{As of now, \github{}'s
  search API can only reflect contents from README file (not other
  code elements).}.  We focused on Java for its popularity.  Although
there is no clearcut limit on number of \github{}
stars~\cite{github-stars} to define an interesting project, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria is a constraint to skip projects without recent activity. The
fourth criteria is an approximation to find Maven projects. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or to test the
project). We used Maven as a reference due to its popularity on Java
projects and to assist one of our experiments. A Maven project may
contain several sub-modules with multiple \pomf{} files but we only
considered projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory and \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example). To ensure that our sample set was stable, we retested
the remaining subjects to eliminate projects with flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists of
\numSubjs{} testable subjects.

@@

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python 3.4, Bash, R and Ruby 2.3 to process the data and generate plots.  All
source artifacts are publicly available for replication (on
request)\Comment{ at \Fix{create gh-pages}}.  This includes supporting
scripts (\eg, the script that test subjects and generates raw analysis
data) and the full list of projects. \Comment{, and a
  \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

To evaluate prevalence of projects with costly test suites, we
considered the \numSubjs{} testable subjects from
Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
the script we used to measure time.  The main loop (lines 5-11)
iterates over the list of subjects and invokes Maven multiple
times\Comment{ to isolate cost of running tests} (lines 7-9).  We
first compiled the source and test files (line 7), made all
dependencies available locally (line 8), and then we ran the tests in
offline mode to skip the package update task (line 9). After
execution, we used a regular expression on the output log to extract
the elapsed time (line 10).

Prior to running this script, we inspected Maven execution logs from a
sample including a hundred projects.  The goal of this inspection step
is to find tasks unrelated to testing (\eg, \emph{javadoc} generation
and static analyses) that could interfere in our measurements.  The
tasks we found were ignored from execution (lines 1-3).  Furthermore,
to avoid noise from operating system events, we configured our
workstation to run only essential services.  The machine was dedicated
to our experiments and we accessed it via SSH. In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment, leaving the remaining CPUs to run OS
processes~\cite{isolcpus-use}.  The rationale for this decision is to
prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared the sequential execution of tests
using Maven with JUnit's default \CodeIn{JUnitCore} runner, invoked
from the command line.  We observed that results were very similar.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As it is to be expected, \longg{} and \medg{} projects do
not occur as frequently as \shortg{} projects.  However, they do occur
in relatively high numbers.  Figure~\ref{fig:rq1-boxplot} shows cost
distribution of test suites in each group as boxplots.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group run in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to observed test failures in some of the
revisions we downloaded.  From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.  Second, some projects may omit
long-running tests on their default execution. For instance, the
project \CodeIn{apache.maven-surefire} runs all unit tests in a few
seconds in our environment.  According to our criteria, this project
would be classified as \shortg{} but we noticed that only smoke test
run by default.  The more expensive integration and system tests are
only accessible via custom parameters.  When running the test suite
with integration tests, the testing time goes to nearly 30 minutes.
For simplicity, we considered only the tests executed by default.

>>>>

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that 100 was enough to eliminate trivial subjects. The third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
  or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from README file (not
other code elements); it does not provide a feature to search for
projects containing certain files in the dir structure (\eg{},
\emph{pom.xml}).  Figure~\ref{fig:subject-query} illustrates the query
to the \github{} API as an HTTP request.  After obtaining a list of
potential projects, we filtered those containing a \pomf{} file in the
root directory.  A Maven project may contain several sub-modules with
multiple \pomf{} files.  We based our methodology to select
experimental subjects on other recent studies in testing and
debugging~\cite{gligoric-etal-issta2015,perez-etal-icst2017}.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
\SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
projects were not Maven or did not have a \pomf{} in the root
directory, \SubjectsGithubNotTestable{} projects were untestable
(because of missing dependencies or incompatible testing environment,
for example), and \SubjectsGithubFlaky{} projects were ``flaky''.  We
executed each project's test suite for three times to identify
projects containing flaky tests that could introduce noise in our
experiments.  Our final set of subjects consists of \numSubjs{}
projects.

@@

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
data and generate plots.  All source artifacts are publicly available
for replication (on request)\Comment{ at \Fix{create gh-pages}}.  This
includes supporting scripts (\eg, the script that test subjects and
generates raw analysis data) and the full list of projects. \Comment{,
  and a \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

To evaluate prevalence of projects with costly test suites, we
considered the \numSubjs{} testable subjects from
Figure~\ref{fig:subjects}.  Figure~\ref{fig:mvn-execution} illustrates
the script we used to measure time.

We tooke the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-3).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

The main loop (lines 5-11) of the script in
Figure~\ref{fig:mvn-execution} iterates over the list of subjects and
invokes Maven multiple times\Comment{ to isolate cost of running
  tests} (lines 7-9).  It first compiles the source and test files
(line 7), make all dependencies available locally (line 8), and then
runs the tests in offline mode as to skip the package update task,
enabled by default (line 9). After execution, we used a regular
expression on the output log to extract elapsed time (line 10).

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.

Figure~\ref{fig:rq1-boxplot} shows cost distribution of test suites in
each group as boxplots.  Note that the y-ranges are different.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

It is important to note that we under-estimated cost in our
experiments for two main reasons.  First, some tests may finish
earlier than expected due to observed test failures in some of the
revisions we downloaded.  From the \numSubjs{} testable projects,
\numSubjsPass{} successfully executed all tests and \numSubjsFail{}
reported some test failures.  Second, some projects may omit
long-running tests on their default execution. For instance, the
project \CodeIn{apache.maven-surefire} runs all unit tests in a few
seconds.  According to our criteria, this project is to be classified
as \shortg{} but a closer look reveals that only smoke tests are run
by default in this project.  Time-consuming integration and system
tests are only accessible via custom parameters, which we do not
handle in our experimental setup.  We enabled such parameters for this
specific project and observed that testing time goes to nearly 30
minutes.  For simplicity, we considered only the tests executed by
default.
